Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-29 paper.tex
update

A recent widely used QoS Evaluation Model, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}. We employ this QoS evluation model and our proposed comprehensive quality evluation model using our proposed PSO-based approach for searching for optimal solutions.
To analyse the differences in optimal solutions found by these two evaluation model, we recorded and compared the different mean values of $SM$ (consisiting of $MT$ and $S$), $QoS$(consisting of $A$, $R$, $T$ and $C$) at the 100th generation of 30 runs. To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using statistical analysis in in Table \ref{decisionTable}.

We observe an interesting pattern from Table \ref{decisionTable}. The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $SM$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evaluation model for all tasks with a slight trade-off in $QoS$.

@@

To better understand a better semantic matchmaking quality with a slight trade-off in the opitmal solutions using comprehensive quality evaluation model, we demonstrate the optimal solutions using task 3 as an example. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as best solutions found by employing QoS evaluation model and comprehensive quality evaluation model respectively. Two approaches generate exactly the same service workflow structure, but some service vertices and edges denoted in red are different. To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge ($sm_{e_1}$ to $sm_{e_4}$) for the two weighted DAGs in Fig. \ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) for the listed qualities using our comprehensive quality evalutaion model. Therefore, an overall gain 0.1433 is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034). Consequently, our comprehensive evaluation model acheive a desirable trade-off in considering both $SM$ and $QoS$. To explain the value of $SM$ gain, we pick up $e_4$ that is associated with a smallest $\Delta Q$. The $e_4$ of $WG(1)$ using QoS evaluation model and $WG(2)$ using comprehensive quality model has two different source service vertices $Ser1640238160$ and $Ser947554374$ respectively,  and the same $end$ vertices. $Ser1640238160$ and $Ser947554374$ are services with concept-related output parameters $Inst795998200$ and $Inst582785907$ corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively, which are marked on the related taxonomy in Fig. \ref{comparisontest} $(4)$. In addtion, $Inst658772240$ is a required parameter of the $end$ vertice as one of composition task outputs, which is related to concept $Con2113572083$. Obviouly,  $Inst795998200$ is closer to user's required output $Inst658772240$ compared to $Inst582785907$.

\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.29]{comparisontest.pdf}}}
 \caption{An example of comparision to optimal solutions using Task 3 for QoS evaluation model and comprehensive evluation model.}
 \label{comparisontest}
\end{figure}

>>>>

Recently, a QoS Evaluation Model, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$, where $\sum_{i=1}^{4} w_i = 1$, is widely used for QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol}. This QoS evluation model is compared to our proposed comprehensive quality evluation model using our proposed PSO-based approach for measuring the effectiveness of our proposed comprehensive quality model. To analyse the differences in optimal solutions found by these two evaluation models, we recorded and compared the different mean values of $SM$ (consisiting of $MT$ and $S$), $QoS$(consisting of $A$, $R$, $T$ and $C$) after 100 generations. To make a sense of the comparison, all these recorded values are normalised from 0 to 1, and compared using independent-samples T tests in Table \ref{decisionTable}.

We observe an interesting pattern from Table \ref{decisionTable}. The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Tasks 2, 3, 4 and 5. However, the mean value of $SM$ using the comprehensive quality evaluation model are significantly higher than those using the QoS evaluation model, while a slight trade-off in $QoS$ are observed in all tasks.

@@

To determine the importance of achieving a good comprehensive quality at the expense of slightly reduced QoS, we demonstrate the best solutions identified by our approach using task 3 as an example. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs obtained by employing the QoS evaluation model and the comprehensive quality evaluation model respectively. Both weighted DAGs have exactly the same service workflow structure, but some service vertices and edges denoted in red are different. To better understand these differences, we list the overall semantic matchmaking quality $SM$,  overall $QoS$ and semantic matchmaking quality associated to each edge ($sm_{e_1}$ to $sm_{e_4}$) in Fig. \ref{comparisontest} $(3)$, where $\Delta Q$ reveals the gain (positive $\Delta Q$) or a loss (negative $\Delta Q$) of the listed qualities for our comprehensive quality evalutaion model. Therefore, an overall gain 0.1433 is calculated from a sum of a $SM$ gain (0.1467) and $QoS$ loss (-0.0034). Consequently, our comprehensive evaluation model acheive a desirable trade-off in considering both $SM$ and $QoS$. To explain the value of $SM$ gain, we pick up $e_4$ that is associated with the smallest $\Delta Q$. The $e_4$ of $WG(1)$ using QoS evaluation model and $WG(2)$ using comprehensive quality model has two different source service vertices $Ser1640238160$ and $Ser947554374$ respectively,  and the same $end$ vertices. $Ser1640238160$ and $Ser947554374$ are services with concept-related output parameters $Inst795998200$ and $Inst582785907$ corresponds to two concepts $Con103314376$ and $Con2037585750$ respectively, which are marked on the related taxonomy in Fig. \ref{comparisontest} $(4)$. In addtion, $Inst658772240$ is a required parameter of the $end$ vertice as one of composition task outputs, which is related to concept $Con2113572083$. Obviouly,  $Inst795998200$ is closer to user's required output $Inst658772240$ compared to $Inst582785907$.

\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.29]{comparisontest.pdf}}}
 \caption{An example of comparision to optimal solutions using Task 3 for QoS evaluation model and comprehensive quality evluation model.}
 \label{comparisontest}
\end{figure}
